---
title: "Start with Coinmarketcapr"
author: "AbdulMajedRaja"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Put the title of your vignette here}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

This vignette is to help you get started with Coinmarketcapr Package that helps to extract and monitor price and market cap of Cryptocurrencies from 'CoinMarketCap' <https://coinmarketcap.com/api/>. Simply, Coinmarketcapr is an R-binding for Coinmarketcap API that lists Price, Marketcap, Transaction Volume of many Cryptocurrencies and tokens. 

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r}
summary(cars)
```

You can also embed plots, for example:

```{r, echo=FALSE}
plot(cars)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
